
##

**Writing an Rmarkdown file**

First create a plain text file and save it as a .Rmd file.

1. Markdown
2. YAML header
3. Code -- chunks and inline
4. [Chunk (knitr) options](https://yihui.name/knitr/options/)

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>


##

**Markdown**

Simple markup language originally designed for quickly making webpages

```
### Header 3

- list item 1
- list item 2
- list item 3

1. enemated item 1
1. enemated item 2
1. enemated item 3

**Bold**, *italicized*, _underlined_ text

```

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>


##

**Markdown**

Simple markup language originally designed for quickly making webpages

<div class="lotsoftext">
### Header 3

- list item 1
- list item 2
- list item 3

1. enemated item 1
1. enemated item 2
1. enemated item 3

**Bold**, *italicized*, ~~strikethrough~~ text

</div>

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>



##

**YAML header**

- YAML is a data serialization language.
- RMarkdown uses it to define document metadata and configuration.
- Should be at the top of the file and preceded and succeeded by three hyphens.


```
---
title: "Example Analysis for Reproducible Reporting Workshop"
author: "Matt Mulvahill"
date: "September 6, 2017"
output: word_document
---
```

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>


## {.codefont}

**Code chunks**

- Started  with three backticks (upper left-most key, below ESC), and open/close
  curly braces.  Chunk is ended with three backticks.
- Within curly braces we denote the 'engine'/language ("r"), a name for the code
  chunk, then any chunk options we want.


<pre><code>```{r my_model_fit, echo=TRUE}
# fit model
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
fit <- lm(mpg ~ cyl, data = mtcars)
```</code></pre>
<pre><code>```{r my_model_summary, echo = TRUE, results='markdown'}
# create summary table
fit %>% broom::tidy(.) %>%
  mutate_at(vars(estimate:statistic), round, digits=2) %>%
  mutate_at(vars(p.value), qwraps2::frmtp) %>% 
  kable
```</code></pre>

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>

## {.codefont}

**Code chunk example**

```{r my_model_fit, echo=TRUE}
# fit model
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
fit <- lm(mpg ~ cyl, data = mtcars)

# extract and format coefficients table
coef_table <- fit %>% broom::tidy(.) %>%
  mutate_at(vars(estimate:statistic), round, digits=2) %>%
  mutate_at(vars(p.value), qwraps2::frmtp, markup = "markup")
```

```{r my_model_summary, echo = TRUE, results='markdown'}
# print formatted coefficients table
coef_table %>%
  kable(., "html", table.attr = "class=\"mytable\"",
        caption = "Table 1. Regression coeffients and related statistics")
```

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>

## {.codefont}

**Inline code example**

- Inline code begins with a backtick and the engine name (r), and ends with a
  single backtick


```{r prepare-inline-stats, echo=TRUE}
# Prepare inline stats from table
coef_6cyl <- coef_table %>% filter(term == 'cyl6') %>% .$estimate
```

**RMarkdown text**

<div class="lotsoftext">
```{r, results='asis', echo=FALSE}
cat("Cars with 6 cylinder engines average `` `r abs(coef_6cyl)` `` lower miles per gallon than 4 cylinder cars.")
```
</div>


**Result**

Cars with 6 cylinder engines average `r abs(coef_6cyl)` lower miles per gallon
than 4 cylinder cars.


<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>


##

**Chunk options**

- Global options are set in a code chunk using `opts_knit$set()`
```{r, eval=FALSE, echo=TRUE}
opts_knit$set(fig.width  = 6,
              fig.height = 4,
              fig.path   = "output/figures/"
              echo       = FALSE,
              warnings   = TRUE,
              messages   = TRUE)
```

- Chunk-specific options are set in the chunk header (must all be on one line)

<pre><code>```{r mychunk, echo=TRUE, results='markup'}</code></pre>

<div class="footer"> Anatomy of an R Markdown file (.Rmd) </div>

