---
title: "Reproducible Reporting with RMarkdown"
author: 
  - Matt Mulvahill
  - Colorado Biostatistical Consortium - Department of Biostatistics - CSPH
date: "9/7/2017"
output: 
  ioslides_presentation:
    css: ../../lib/styles.css
  md_document:
    variant: markdown_github
bibliography: ../../lib/references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r notes, echo=FALSE}
## Overview
# 
# 1. Overview of the Aspects of Reproducible Research (link to ASA doc)
# 1. Basic Guidelines for Scientific Computing  (folder structure, relative paths, etc.)
# 1. Reproducible Reporting -- What is it?
# 1. Motivating Examples (patients added, data revised, reviewer questions, reader questions)
# 1. Use Scenarios -- Analysis notebooks, analysis reports, manuscript, other (presentations, web pages, etc.)
# 1. Technologies/Tools ("pipelines") (Rmd -> md -> html/doc/pdf/ )
# 1. Rmarkdown via RStudio
#
```

## Prereqs -- Software to install

**Test software install on fresh computer**

- [R](https://cloud.r-project.org/)
- [RStudio](https://www.rstudio.com/products/rstudio/download/#download) 

And if you are not using RStudio, you will also need these:

- `rmarkdown` package: `install.packages("rmarkdown")`
- `knitr` package: `install.packages("knitr")`	
- [pandoc](https://pandoc.org/installing.html)


# Defining Reproducibility



## 

<div class="verticalcenterdiv">
- Reproducibility
    - “A study is reproducible if you can take the original data and the computer
      code used to analyze the data and reproduce all of the numerical findings
      from the study.”
<br>
<br>
<br>
- Replicability
    - “...the act of repeating an entire study, independently of the original
      investigator without the use of original data (but generally using the same
      methods).”
</div>

<div class="footer"> ASA Recommendations to Funding Agencies Supporting Reproducible Research - @Broman2017</div>




<!-- ****************************************** -->
<!-- ******* Start of Principles series ******* -->
<!-- ****************************************** -->

<!-- ** 1.   ********************************** -->
## 

**Principles of Reproducibility**

<div class="lotsoftext">

- Ideally, the use of ***publicly available data***.
- Use of ***version control*** for all code development.
- Exclusive use of ***open-source software***, freely available worldwide.
- ***End-to-end scripting*** of research (data processing/cleaning, statistical analyses,
	visualizations, and ***report/manuscript generation***) with full workflow made
	available to others.
- Use of ***container/virtual machine tools*** to capture software versions,
	dependencies, and platform specifics.
- ***Publication of code*** in public repositories, as with data.
- Implementing algorithms on standard computational platforms (R/Python
	packages, etc.)
</div>

<div class="footer"> ASA Recommendations to Funding Agencies Supporting Reproducible Research - @Broman2017</div>


<!-- ** 2.   ********************************** -->
## 

**Principles of Reproducibility -- HIPAA**

<div class="lotsoftext">

- Ideally, the use of ***publicly available data***.
- <div class="gray">Use of ***version control*** for all code development.</div>
- <div class="gray">Exclusive use of ***open-source software***, freely available worldwide.</div>
- <div class="gray">***End-to-end scripting*** of research (data processing/cleaning, statistical analyses,
	visualizations, and ***report/manuscript generation***) with full workflow made
	available to others.</div>
- <div class="gray">Use of ***container/virtual machine tools*** to capture software versions,
	dependencies, and platform specifics.</div>
- ***Publication of code*** in public repositories, as with data.
- <div class="gray">Implementing algorithms on standard computational platforms (R/Python
	packages, etc.)</div>

</div>

<div class="footer"> ASA Recommendations to Funding Agencies Supporting Reproducible Research - @Broman2017</div>


<!-- ** 3.   ********************************** -->
## 

**Principles of Reproducibility -- Advanced tools**

<div class="lotsoftext">

- <div class="gray">Ideally, the use of ***publicly available data***.</div>
- <div class="gray">Use of ***version control*** for all code development.</div>
- <div class="gray">Exclusive use of ***open-source software***, freely available worldwide.</div>
- <div class="gray">***End-to-end scripting*** of research (data processing/cleaning, statistical analyses,
	visualizations, and ***report/manuscript generation***) with full workflow made
	available to others.</div>
- Use of ***container/virtual machine tools*** to capture software versions,
	dependencies, and platform specifics.
- <div class="gray">***Publication of code*** in public repositories, as with data.</div>
- Implementing algorithms on standard computational platforms (R/Python
packages, etc.)

</div>

<div class="footer"> ASA Recommendations to Funding Agencies Supporting Reproducible Research - @Broman2017</div>


<!-- ** 4.   ********************************** -->
## 

**Principles of Reproducibility -- Our Toolkit**

<div class="lotsoftext">

- <div class="gray">Ideally, the use of ***publicly available data***.</div>
- Use of ***version control*** for all code development.
- Exclusive use of ***open-source software***, freely available worldwide.
- ***End-to-end scripting*** of research (data processing/cleaning, statistical
	analyses, visualizations, and ***report/manuscript generation***) with full workflow
	made available to others.
- <div class="gray">Use of ***container/virtual machine tools*** to capture software versions,
	dependencies, and platform specifics.</div>
- <div class="gray">***Publication of code*** in public repositories, as with data.</div>
- <div class="gray">Implementing algorithms on standard computational platforms (R/Python
	packages, etc.)</div>

</div>

<div class="footer"> ASA Recommendations to Funding Agencies Supporting Reproducible Research - @Broman2017</div>

<!-- ****************************************** -->
<!-- ******** End of Principles series ******** -->
<!-- ****************************************** -->


## 

<div class="emphasized verticalcenterdiv">
1. Scientific computing basics
1. Reproducible reports
1. Version control
</div>

<div class="footer"> . </div>

#

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

