---
title: "Reproducible Reporting with RMarkdown"
author: 
  - Matt Mulvahill
  - Colorado Biostatistical Consortium - Department of Biostatistics - CSPH
date: "9/7/2017"
output: 
  ioslides_presentation:
    css: lib/styles.css
    logo: lib/images/cctsi_logo.png
  md_document:
    variant: markdown_github
bibliography: lib/references.bib
---


```{r workspace-setup, include=FALSE}
# Package and environ options
options(scipen = 99)
options(stringsAsFactors = FALSE)
options(width = 300) # specific to my monitors/working environment

# Load packages
library(tidyverse)
library(knitr)
library(rmarkdown)
```

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(fig.path   = 'output/figures/',
                      fig.align = "center",
                      cache      = FALSE,
                      echo       = FALSE,
                      message    = TRUE,
                      warning    = TRUE)
knitr::opts_knit$set(eval.after = c("fig.cap"))
```



<!--
## Overview
# 
# X 1. Overview of the Aspects of Reproducible Research (link to ASA doc)
# X 1. Basic Guidelines for Scientific Computing  (folder structure, relative paths, etc.)
# 1. Reproducible Reporting - What is it?
# 1. Motivating Examples (patients added, data revised, reviewer questions, reader questions)
# 1. Use Scenarios - Analysis notebooks, analysis reports, manuscript, other (presentations, web pages, etc.)
# 1. Technologies/Tools ("pipelines") (Rmd -> md -> html/doc/pdf/ )
# 1. Rmarkdown via RStudio
#
-->


## Materials

http://github.com/mmulvahill/rr_workshops.git



## Prereqs -- Software to install

**Test software install on fresh computer**

- [R](https://cloud.r-project.org/)
- [RStudio](https://www.rstudio.com/products/rstudio/download/#download) 

**If you are not using RStudio, you will also need these:**

- [pandoc](https://pandoc.org/installing.html)
- `rmarkdown` package
- `knitr` package

```{r eval=FALSE, echo=TRUE}
install.packages(c("rmarkdown", "knitr"))
```

## Additional tools used in this presentation

```{r addl-pkgs, eval=FALSE, echo=TRUE}
install.packages(c("tidyverse", "broom", "babynames"))
```


# Defining Reproducibility

```{r intro, child="Rmd/01_introduction.Rmd"}
```

# Scientific computing basics

```{r scicomp, child="Rmd/02_computing_basics.Rmd"}
```

# Reproducible reporting

```{r reproduciblereports, child="Rmd/03_intro_to_reporting.Rmd"}
```

# RMarkdown

```{r rmarkdown, child="Rmd/04_rmarkdown.Rmd"}
```

# Hands-on Example

```{r rmdexample, child="Rmd/05_rmdexample.Rmd"}
```

# Advanced topics

```{r rmdexample, child="Rmd/06_advanced.Rmd"}
```


## 

- [RStudio's RMarkdown website](http://rmarkdown.rstudio.com/lesson-1.html)
- [knitr's website](https://yihui.name/knitr/)
- [Karl Broman's RMarkdown
  guide](http://kbroman.org/datacarpentry_R_2016-06-01/05-rmarkdown.html)
- [Reproducible web documents with R, knitr, & Markdown](http://cpsievert.github.io/slides/markdown/#/)


<div class="footer"> Useful links </div>

## 

<div class="footer"> References </div>



```{r compile-doc, eval=FALSE, include=FALSE}
render("reporting_presentation.Rmd", output_format = "all")
```
